RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
added another thing to add to the intro

- Rapid growth in phylogenetics data (+citations)
- Rapid growth of research methods and software that use phylogenetic data. Comparative methods in evolution. Ecological phylogenetics. Biodiversity informatics. (+citations)
- More on data sharing challenges and opportunities a la @Drew_2013

>>>>

- Rapid growth in phylogenetics data (+citations)
- Rapid growth of research methods and software that use phylogenetic data. Comparative methods in evolution. Ecological phylogenetics. Biodiversity informatics. (+citations)
- More on data sharing challenges and opportunities a la @Drew_2013
- More on the hoops that users need to jump through if trees, data
and other things all need to come from separate files and need to be
joined on taxon labels.
